Barriers to Green Living: Insights from 2018 and 2021 Toronto Climate Perception Surveys

### 2024-12-03 paper/climate_change.qmd
changes upon rendering

```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-one
#| fig-cap: The histogram shows the distribution of age given the 2018 survey respondents.

@@

```{r}
#| warning: false
#| echo: false
#| message: false
#| label: table-one
print(age_summary_combined)

@@

### Highest Level of Education Completed
#### Individual 2018
@fig-two illustrates the distribution of survey respondents by their highest level of education attained. The most frequently reported education levels are "Completed undergraduate degree" and "Post graduate/professional school," with both categories having a noticeably higher frequency compared to others, indicating a well-educated respondent population. In contrast, fewer respondents reported "Some community college, vocational, trade school" and "Completed community college, vocational, trade school," suggesting these levels are less common among participants. Additionally, a small portion of respondents preferred not to disclose their education level. This distribution highlights a skew toward higher educational attainment within the sample, which may influence responses related to socio-economic factors and other survey topics.
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-two
#| fig-cap: The histogram shows the distribution of education levels of 2018 survey respondents.

@@

```
#### Comparison 2018 to 2021
@table-two illustrates respondant education level in 2018 and 2021 respectively. Please note, the categories of education level are different for 2018 and 2021 as these were different surveys and categories were updated in 2021. Despite this, we are still able to make comparisons. Individuals with high school diplomas or less account for 9 for 2018 and 38 for 2021 (addition of less than highs school and high school or equivalent categories). This could indicate that the younger population was included more in the 2021 suvey or that less education individuals were surveyed. Additionally, its not super clear howver those with a post graduate or professional degree accounted for 29 percent in 2018 and 35 percent in 2021. This illustrates that more educated inviduals responded to the 2021 survey.
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: table-two
#| fig-cap:?

print(education_summary_combined)
```

@@

```{r}
#| warning: false
#| echo: false
#| message: false
#| label: table-three
#| fig-cap:?

print(informed_summary_combined)
```

@@

```{r}
#| warning: false
#| echo: false
#| message: false
#| label: table-four
#| fig-cap:?

print(communication_summary_combined_table)
```
### Likelihood Taking Action
#### Individual 2018
The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors. 
@fig-five illustrates self-reported likelihood of taking certain actions that minimize climate change effects. On the x-axis, we have the nine different climate actions and on the y-axis is the percentage. The stacked bar chart allows understanding of how likely individuals are to take part in the given actions. 
Sorting waste into the correct bins is the action that most individuals are doing right now, accounting for 60 percent whith 24 percent saying they are very likely to take part in this action. The next most prominent actions are walking or cycling short distances, reduce hydro usage, reduce waste and home improvements. 40 percent of invidiuals report walking or cycling when traveling shorter distances in the city with 22 percent reporting they are very likely. However, 7 percent say they are very unlikely to change their method of transportation. Reducing the amount of energy and water use is already done by 36 percent and very likely for 29 percent only a mere 3 percent is very unlikely. Reducing personal waste such as contributing to repurposing used products has similar percentages to responses for reducing hydro but even fewer individuals that report they are very unlikely to take action. Similarly, the likelihoods for making home improvements for energy efficiency such as energy-efficient appliances, programmable thermostat, LED lightbulbs, green or cool roof. 
In contrast, the action where the least number of individuals are contributing to is the investment of an electric or hybrid vehicle over gas-powered vehicles with only 8 percent who currently have an energy efficient vehicle. While 19 percetn are very likely to make this switch, 14 percent say they are very unlikely. This illustrates that buying an electric or hybrid vehicle is action the least number of individuals are willing to invest in despite gas-powered vehicles being a major contributor to greenhouse gases. This action has a huge impact on the environment and yet 41 percent of this sample say they are unlikely to change! The second action that individuals are most unlikely to engage in is eat less meat by incorporating more plant-based foods in their diet with 12 percent very unlikely and 23 percent somewhat unlikely. Only 23 percent are already consuming meat alternatives. Vegans greenhosue gas emissions are on average 37% lower than those who eat meat frequently. 
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-five
#| fig-cap: The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change.

@@

knitr::include_graphics(here("data/03-figures_data", "likelihood_age_plot.png"))
```

@@

```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-seven
#| print(likelihood_education_plot)
```

>>>>

```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-one
#| fig-cap: "The histogram shows the distribution of age given the 2018 survey respondents."

library(here)

@@

```{r}
#| warning: false
#| echo: false
#| message: false
# #| label: table-one
# #| fig-cap: "Comparison of Age Distribution Between 2018 and 2021 Surveys: This table highlights the age distribution of survey respondents in 2018 and 2021. Notable differences include a higher representation of individuals aged 18–23 in 2021 compared to 2018, while the distribution across other age groups remained relatively consistent between the two years."

# Read the cleaned CSV into a data frame
# age_summary_combined <- read.csv(here("data/03-figures_data", "age_summary_combined.csv"))

# Print the cleaned table (using kable for styling)
# age_summary_combined %>%
  # kbl(caption = "Age Distribution Comparison for 2018 and 2021") %>%
  # kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover", "condensed"))

@@

### Highest Level of Education Completed
#### Individual 2018
@fig-two illustrates the distribution of survey respondents by their highest level of education attained. The most frequently reported education levels are "Completed undergraduate degree" and "Post graduate/professional school," with both categories having a noticeably higher frequency compared to others, indicating a well-educated respondent population. In contrast, fewer respondents reported "Some community college, vocational, trade school" and "Completed community college, vocational, trade school," suggesting these levels are less common among participants. Additionally, a small portion of respondents preferred not to disclose their education level. This distribution highlights a skew toward higher educational attainment within the sample, which may influence responses related to socio-economic factors and other survey topics.
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-two
#| fig-cap: "The histogram shows the distribution of education levels of 2018 survey respondents."

@@

```
#### Comparison 2018 to 2021
@table-two illustrates respondant education level in 2018 and 2021 respectively. Please note, the categories of education level are different for 2018 and 2021 as these were different surveys and categories were updated in 2021. Despite this, we are still able to make comparisons. Individuals with high school diplomas or less account for 9 for 2018 and 38 for 2021 (addition of less than highs school and high school or equivalent categories). This could indicate that the younger population was included more in the 2021 suvey or that less education individuals were surveyed. Additionally, its not super clear howver those with a post graduate or professional degree accounted for 29 percent in 2018 and 35 percent in 2021. This illustrates that more educated inviduals responded to the 2021 survey.
```{r}
#| warning: false
#| echo: false
#| message: false
# #| label: table-education
# #|  fig-cap: TODO

# Load necessary libraries
# library(tinytable)

# Read the CSV into a data frame
# education_summary_combined <- read.csv(here("data/03-figures_data", "education_summary_combined.csv"))

# Remove the leading 'X' from column names
# colnames(education_summary_combined) <- gsub("^X", "", colnames(education_summary_combined))

# Convert the data frame to tinytable
# education_summary_combined_tiny <- tt(education_summary_combined)

# Print the tinytable
# education_summary_combined_tiny

@@

```{r}
#| warning: false
#| echo: false
#| message: false
# #| label: table-three
# #| fig-cap: TODO

# print(informed_summary_combined)
```

@@

```{r}
#| warning: false
#| echo: false
#| message: false
# #| label: table-four
# #| fig-cap: TODO

# print(communication_summary_combined_table)
```
### Likelihood Taking Action
#### Individual 2018
The likelihood of taking action against climate change was explored by assessing individuals' intentions and behaviors. 
@fig-five illustrates self-reported likelihood of taking certain actions that minimize climate change effects. On the x-axis, we have the nine different climate actions and on the y-axis is the percentage. The stacked bar chart allows understanding of how likely individuals are to take part in the given actions. 
Sorting waste into the correct bins is the action that most individuals are doing right now, accounting for 60 percent whith 24 percent saying they are very likely to take part in this action. The next most prominent actions are walking or cycling short distances, reduce hydro usage, reduce waste and home improvements. 40 percent of invidiuals report walking or cycling when traveling shorter distances in the city with 22 percent reporting they are very likely. However, 7 percent say they are very unlikely to change their method of transportation. Reducing the amount of energy and water use is already done by 36 percent and very likely for 29 percent only a mere 3 percent is very unlikely. Reducing personal waste such as contributing to repurposing used products has similar percentages to responses for reducing hydro but even fewer individuals that report they are very unlikely to take action. Similarly, the likelihoods for making home improvements for energy efficiency such as energy-efficient appliances, programmable thermostat, LED lightbulbs, green or cool roof. 
In contrast, the action where the least number of individuals are contributing to is the investment of an electric or hybrid vehicle over gas-powered vehicles with only 8 percent who currently have an energy efficient vehicle. While 19 percetn are very likely to make this switch, 14 percent say they are very unlikely. This illustrates that buying an electric or hybrid vehicle is action the least number of individuals are willing to invest in despite gas-powered vehicles being a major contributor to greenhouse gases. This action has a huge impact on the environment and yet 41 percent of this sample say they are unlikely to change! The second action that individuals are most unlikely to engage in is eat less meat by incorporating more plant-based foods in their diet with 12 percent very unlikely and 23 percent somewhat unlikely. Only 23 percent are already consuming meat alternatives. Vegans greenhosue gas emissions are on average 37% lower than those who eat meat frequently. 
```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-five
#| fig-cap: The stacked bar plot shows the likelihood of survey respondents taking various actions to address climate change.

@@

knitr::include_graphics(here("data/03-figures_data", "likelihood_age_plot.png"))

@@

```{r}
#| warning: false
#| echo: false
#| message: false
#| label: fig-seven

knitr::include_graphics(here("data/03-figures_data", "likelihood_education_plot.png"))
